A Case Study in Preserving a High Energy Physics Application

### 2014-03-14 paper.tex
modify figure 1 and table 1

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & HDFS& 24TB & 43.3GB & 20GB \\ \hline
        CMSSW binaries     & local & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 51MB & 51MB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Cern files & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        NDCMS & NFS & 862GB & N/A & 53KB \\ \hline
        Local store & AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 180.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 73.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 51MB & 51MB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 41KB \\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.3MB \\ \hline     
        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        HOME dir& AFS &10.2GB & N/A & 34MB\\ \hline
        Total      &    & 180.1TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of acutally used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}
